quollr: An R Package for Visualizing $2-D$ Models from Non-linear Dimension Reductions in High Dimensional Space

### 2024-06-22 paper-quollr.Rmd
Add removing long edge threshold explanation

>>>>

In some cases, distant centroids may be connected, resulting in long line segments that can affect the smoothness of the $2\text{-}D$ representation. To address this issue, the `find_lg_benchmark()` function is used. This function computes a threshold based on the distances of line segments, determining when long edges should be removed.
